% Document class options:
% 11pt for 11 point font
\documentclass[11pt, oneside, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[hypertexnames=false]{hyperref} 
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,      
    urlcolor=cyan,
}

\urlstyle{same}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{array}


% Set spacing (i set it to 1.2x)
\renewcommand{\baselinestretch}{1}
% Indentation (set this to zero for normal prose)
\setlength{\parindent}{0em}
% Line breaking (spacing between paragraphs)
\setlength{\parskip}{0.5em}

% Use the whole page
\usepackage{geometry}
% Extra math glyphs
\usepackage{amsmath}
% Proper enumerate spacing
\usepackage{enumitem}
% More pleasing screen fonts
\usepackage{lmodern}
% Fancy headers
\usepackage{fancyhdr}
\usepackage{graphicx}
% Allows absolute positioning of images
\usepackage{float}
% \usepackage[section]{placeins}
% Set no separation
\setlist{noitemsep}
% Set margins to reasonable
\geometry{margin=2.5cm}
% Sets graphics path
\graphicspath{ {./images/} }
% Sets up fancy headers

\addto\captionsenglish{
\renewcommand{\listfigurename}{List of Images}
}

\usepackage{listings}
\usepackage{color}

\pagestyle{plain}

\begin{document}


\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Python,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

\pagestyle{fancy}
\fancyhf{}
\lhead{Natalie Hong - Computer Networks 1}
\rhead{COMS3200}

\section*{Part A}
\subsection*{Scenario 1}
\subsubsection*{Question 1}
1153.3333

\subsubsection*{Question 2}
1940

\subsection*{Scenario 2}
\href{https://docs.google.com/spreadsheets/d/1m2-pIAhmZVawWgiLYZ5HToiAK6Jz3EaOimxeTKg2bok/edit?usp=sharing}{Excel Sheet}

\subsubsection*{Question 1}
252.5634143

\subsubsection*{Question 2}
505.1268286

\subsubsection*{Question 3}
741.6902429

\subsubsection*{Question 4}
978.2536571

\subsubsection*{Question 5}
2243.6225

\subsubsection*{Question 6}
3508.991343

\subsubsection*{Question 7}
10366.1342

\subsubsection*{Question 8}
11312.38786

\subsection*{Scenario 3}
\subsubsection*{Question 1}
1, 8 

\subsubsection*{Question 2}
2,3,4,5,6,7

\subsubsection*{Question 3}
NS

\subsubsection*{Question 4}
NS

\subsubsection*{Question 5}
A

\newpage
\section*{Part B}

\subsection*{Question 1: What is the web browser being used by the sender?}
Mozilla Firefox

\subsection*{Question 2: What is the web server software being used in the remote server?}
Server: Microsoft-ISS 7.0

\subsection*{Question 3: Is protocol offloading being used at the client?}
No it is not

\subsection*{Question 4: How many routers are there between the client and server?}
8

\subsection*{Question 5: What is the raw TCP sequence number of}

  \subsubsection*{a) the packet initiating the TCP connection?}
  Sequence Number (raw): 3851697578
  \subsubsection*{b) the acknowledgement from the server for the above packet?}
  Sequence Number (raw): 2747564191

\subsection*{Question 6: In frame 4, what are the values of the 8 TCP flags (CWR to FIN) as a single 8-digit binary number?}
00011000

\subsection*{Question 7: In frame 4, the GET request is for a javascript file resource. What is the address of the web page that requested this javascript file resource?}
http://a.bcd.com

\subsection*{Question 8: How long should the received javascript file be considered fresh?}
101

\subsection*{Question 9: What is the initial value of the window scale shift count indicated by}
    \subsubsection*{a) the client?}
    7

    \subsubsection*{b) the server?}
    5

\subsection*{Question 10: The GET packet from the client to the server has an advertised window size of 46. What is the true value window size in bytes?}
5888 Bytes

\subsection*{Question 11: How many bytes are lost totally while tranmissing is indicated in the pcapfile?}
1448

\subsection*{Question 12: How  many  duplicate  acknowledgments  are  sent  by  the  client  regarding the missing bytes?}
3

\subsection*{Question 13: In which frame is the lost frame retransmitted?}
38

\subsection*{Question 14: In  which  frame  does  the  receiver  indicate  that all  missing  frames  have  been received?}
39

\subsection*{Question 15: From frame 1 to 3(inclusive), how many frames have incorrect checksum value?}
0

\end{document}

















